Items: English

### 2021-11-03 analyses.RmD
- updates before sending to Nik

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F, cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 120)
```

@@

```{r r-setup}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

@@

Order dataset. First waves, then id.

```{r}
d_long %<>%
  arrange(wave, id)
```

@@

```{r}
model_soc_med_post <- lmer(soc_med_post ~ (1 | id) + (1 | wave), d_long)
fig_soc_med_post <- make_graph(model_soc_med_post, "Social Media Posting", ll = 1, ul = 5)
fig_soc_med_post
```

@@

```{r}
model_1 <- lmer(life_sat ~ (1 | id) + soc_med_fb + soc_med_ig + soc_med_wa + soc_med_yt + soc_med_tw,
                data = d_long)
summary(model_1)
```

@@

```{r}
model_2 <- lmer(life_sat ~ (1 | id) + (1 | wave) + soc_med_read_b + soc_med_read_w + soc_med_like_share_b + soc_med_like_share_w + soc_med_post_b + soc_med_post_w + soc_med_fb_b + soc_med_fb_w + soc_med_ig_b + soc_med_ig_w + soc_med_wa_b + soc_med_wa_w + soc_med_yt_b + soc_med_yt_w + soc_med_tw_b + soc_med_tw_w,
                data = d_long)
summary(model_2)
```

>>>>

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 120)
```

@@

```{r r-setup, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

@@

Order dataset. First id, then wave.

```{r}
d_long %<>%
  arrange(id, wave)
```

@@

```{r}
model_soc_med_post <- lmer(soc_med_post ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_post)
fig_soc_med_post <- make_graph(model_soc_med_post, "Social Media Posting", ll = 1, ul = 5)
fig_soc_med_post
```

@@

```{r}
model_1 <- lmerTest::lmer(life_sat ~ (1 | id) + soc_med_read + soc_med_like_share + soc_med_post + soc_med_fb + soc_med_ig + soc_med_wa + soc_med_yt + soc_med_tw,
                data = d_long)
summary(model_1)
```

@@

```{r}
model_2 <- lmerTest::lmer(life_sat ~ (1 | id) + (1 | wave) + soc_med_read_b + soc_med_read_w + soc_med_like_share_b + soc_med_like_share_w + soc_med_post_b + soc_med_post_w + soc_med_fb_b + soc_med_fb_w + soc_med_ig_b + soc_med_ig_w + soc_med_wa_b + soc_med_wa_w + soc_med_yt_b + soc_med_yt_w + soc_med_tw_b + soc_med_tw_w,
                data = d_long)
summary(model_2)
```

### 2021-11-03 items_english.rmd
- updates before sending to Nik

## Social media use: Reading

"Wie oft haben Sie letzte Woche die folgenden Aktivitäten in Sozialen Netzwerken gesetzt?"

 - "Postings anderer lesen, in denen es um Inhalte zum Coronavirus geht"

## Social media use: Liking & Sharing

"Wie oft haben Sie letzte Woche die folgenden Aktivitäten in Sozialen Netzwerken gesetzt?"

 - "Bei Postings anderer zum Coronavirus auf den „Gefällt mir“ Button drücken, „teilen“ oder „retweeten“"

## Social media use: Active Postings

"Wie oft haben Sie letzte Woche die folgenden Aktivitäten in Sozialen Netzwerken gesetzt?"

 - "Selbst Postings zum Coronavirus in Sozialen Netzwerken verfasst"

## Social media use: Specific platforms

"Wie oft in der letzten Woche haben Sie Informationen zur Corona-Krise in den folgenden Sozialen Medien verfolgt?"

@@

>>>>

## Social media use

"How often during the last week have you engaged in the following activities on social media?"

(1 = several times per day; 2 = daily; 3 = several times per week; 4 = weekly; 5 = never)

### Reading

 - "Reading the posts of others with content on the Coronavirus."

### Liking & Sharing

 - "When seeing Posts on the Coronavirus, I clicked "like", "share" or "retweet".

### Active Postings

 - "I myself wrote posts on the Coronavirus on Social Media."

### Specific platforms

"How often in the last week have you followed information related to the Corona-crisis in the following social media?"

@@

(1 = several times per day; 2 = daily; 3 = several times per week; 4 = weekly; 5 = never)
